---
title: "Crpyto Charts"
author: "Nick Hatley"
date: 2018-03-03T20:50:11-05:00
categories: ["R"]
output:
  html_document:
      highlight: tango
  theme: cosmo
tags: ["R Markdown"]
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning =  FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.align = 'center')
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(fig.height = 8)
options(knitr.table.format = "html") 
```


```{r get librarys, function and data}
library(tidyverse)
library(plotly)
library(knitr)
library(kableExtra)

bitstamp_btc_usd = "BITSTAMP_SPOT_BTC_USD"
bitstamp_eth_usd = "BITSTAMP_SPOT_ETH_USD"
bitstamp_ltc_usd = "BITSTAMP_SPOT_LTC_USD"
bitstamp_xrp_usd = "BITSTAMP_SPOT_XRP_USD"
bitstamp_bch_usd = "BITSTAMP_SPOT_BCH_USD"

coins = list(bitstamp_btc_usd, bitstamp_eth_usd, bitstamp_ltc_usd, 
             bitstamp_xrp_usd, bitstamp_bch_usd)

all_data = read_rds("data/historical/btc_eth_ltc_xrp_bch.rds")

make_ohlc_candlestick_md <- function(symbol_in, time_frame) {
    df2 = all_data %>%
    filter(duration==time_frame) %>% 
    filter(symbol==symbol_in) 
      
    p = df2 %>% 
    plotly::plot_ly(x = ~time_open, y = ~price_close, type="candlestick",
            open = ~price_open, close = ~price_close,
            high = ~price_high, low = ~price_low) %>%
    plotly::add_lines(x = ~time_open, y = ~price_close, 
              line = list(color = 'black', width = 0.75), inherit = F) %>%
    plotly::layout(showlegend = FALSE) %>% 
    plotly::layout(title = paste0(symbol_in))
    
}
```

## Cryptocurrency Candlestick Charts
If you aren't keen on finance or if you are new to these kinds of charts, as I was, I'll explain them briefly:

>Each individual bars reoresent a day. The low point of the bars represent the low-point for the coin that day and so forth for the high/high point. The coloring represents where the coin closed that day in respect to the prior day. Red = below, Green = above.

The charts are interactive and they include a 'rangeslider' on the bottom that allows you to zoom into specific time-spans.

The tabs allow you to start from different time outlooks.  

##{.tabset .tabset-fade .tabset-pills}
### Six months
```{r, six_months, }
six_months = map(coins, function(x) 
  make_ohlc_candlestick_md(symbol = x, time_frame = "six_months")) 
htmltools::tagList(six_months)
```
